Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 relatedwork.tex
oops

{\bf VisMashup}~\cite{Santos:2009:VST} VisMashup defines a schema and
semantics for automatically deriving user interfaces from workflows,
while Crowdlabs exposes these capabilities on a website
feature~\cite{Mates:2011:CSA} workflow upload and remote execution. In
our view, the impedance mismatch between a dataflow pipeline
specification and the power of a general-purpose language is too great
for the type of general exploratory work in data science teams. At the
expense of ease of use for non-programmers, RCloud tries to provide a
closer match for analysts accustomed to creating and executing R and
Python code, while retaining attractive properties like transparent
provenance tracking and interactive data visualization on the web.

>>>>

VisMashup~\cite{Santos:2009:VST}  defines a schema and
semantics for automatically deriving user interfaces from workflows,
while Crowdlabs exposes these capabilities on a website
feature~\cite{Mates:2011:CSA} workflow upload and remote execution. In
our view, the impedance mismatch between a dataflow pipeline
specification and the power of a general-purpose language is too great
for the type of general exploratory work in data science teams. At the
expense of ease of use for non-programmers, RCloud tries to provide a
closer match for analysts accustomed to creating and executing R and
Python code, while retaining attractive properties like transparent
provenance tracking and interactive data visualization on the web.
